---
output: word_document
params:
  title: "Motor Trend Car Road Tests"
  author: ""
  date: "2017-04-20"
  data: ""
  varx: ""
  desx: ""
  vary: ""
  desy: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(pander)

# setting dataset
d <- get(params$data)
dt <- d[c(params$varx, params$vary)]

# PAnder table configuration
panderOptions('table.alignment.default', function(df)
    ifelse(sapply(df, is.numeric), 'right', 'left'))
panderOptions('table.alignment.rownames', 'left')
panderOptions('table.emphasize.rownames', F)
panderOptions('table.style', 'grid')
panderOptions('big.mark', ",")
panderOptions('keep.trailing.zeros', TRUE)
panderOptions('table.continues', '')

```

### `r sprintf('%s', params$title)`

**Autor**: `r sprintf('%s', params$author)`

**Fecha**: `r sprintf('%s', params$date)`


<br><br>

#### Description of data

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles (1973–74 models).

<br><br>

- **Variables**: The format of the data comes gave as by following structure:
    - **`r sprintf('%s', params$varx)`**: `r sprintf('%s', params$desx)`
    - **`r sprintf('%s', params$vary)`**: `r sprintf('%s', params$desy)`

<br><br>

#### Including Tables

You can display nice tables into report. The table bellow is the 10-row header of data, printed using the **`pander`** r package:

<br><br>

```{r table}
pander(head(dt, 10L))
```

<br><br>

#### Including Plots

... And you can plot using the great potential that have R to do it.

<br><br>

```{r plot, fig.width=8}
ggplot(dt, aes_(x = as.name(params$varx), as.name(params$vary))) + geom_point() + theme_bw()
```